### 2023-08-30 appendixPN.tex
up

\begin{samepage}
{\bf Construction of $N_2$} \\
\indent
The reset Petri net $N_2$ is constructed from $N_1$ by the addition of two places $p_1$ and $p_2$ and $|P_1| +2$ transitions $t_{p_1}$, $\{ t_p \mid p \in P_1 \}$ and $t_{p_2}$.
We first modify all transitions of $N_1$ to include $p_1$ as both an input and an output.
The initial marking $\mu_2$ will include a token in $p_1$ and no token in $p_2$. 
This new place $p_1$ serve to mark that the run is ongoing. As long as it contains a token, the adjusted transitions of $N_1$ are live and can be used normally. Thus any marking which is reachable in the places of $N_1$ is also reachable in the corresponding places of $N_2$.
We add an additional transition $t_{p_1}$ %\alain{s est d'habitude un état}
which has $p_1$ as an input and a null output.
This allows to disable the transitions of $N_1$ and to "freeze" the marking of the places of $P_1$ in $N_2$.
 The place $p_1$ and transition $t_{p_1}$ allow the net $N_2$ to reach any reachable marking in $N_1$ and then for $t_{p_1}$ to fire and freeze the net at that marking.
We introduce a new place $p_2$ and new transitions $t_p$, for all $p \in P_1$, which have $p$ as input and $p_2$ as output.
Lastly, we add a transition $t_{p_2}$ with $p_2$ as its output and every place of $P_2$ as output, which ``floods'' the net with tokens, assuring that every transition is live if a token is ever
put in $p_2$.
\end{samepage}

@@

Indeed the marking with zero in every place of $P_1$ and in $p_2$ is reachable in $N_2$, by executing the same sequence of transition firings. Then $t_{p_1}$ can fire, leading to the marking which assigns zero to every place of $P_2$. From this marking the transitions $t_p$ are not live and neither are the transitions inherited from $N_1$ nor $t_{p_1}$, and, finally, nor is $t_{p_2}$. Thus $t_{p_2}$ is not live. \\

@@

Indeed, if $t_{p_2}$ is not live, then a marking $\mu$ must be reachable in which $\mu(p_2) = 0$ and there is no reachable state in which $p_2$ has a token (in particular, since we do not allow token removal from $p_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $p_2$).
This means that no transition $t_p$ is live in $\mu$ since any transition $t_p$ can place a token in $p_2$. 
Thus, every place of $P_2$ inherited from $N_1$ must be devoid of token. Moreover, since the marking $\mu$ must be reached  in a sequence of transitions that do not place any token in $p_2$, 
it can be reached without using the transitions $t_p$ or $t_{p_2}$. Since $t_{p_1}$ do not modify the places inherited from $P_1$ nor does it enable new transitions, the reachability of $\mu$ implies the reachability of a marking where every place of $P_2$ inherited from $P_1$ is devoid of token using only the transitions inherited from $N_1$. Thus the zero marking is reachable from $\mu_1$ in $N_1$.
\end{proof}

>>>>

\begin{samepage}
{\bf Construction of $N_2$} \\
\indent
The reset Petri net $N_2$ is constructed from $N_1$ by the addition of two places $p_a$ and $p_b$ and $|P_1| +2$ transitions $t_{p_a}$, $\{ t_p \mid p \in P_1 \}$ and $t_{p_b}$.
We first modify all transitions of $N_1$ to include $p_a$ as both an input and an output.
The initial marking $\mu_2$ will include a token in $p_a$ and no token in $p_b$. 
This new place $p_a$ serve to mark that the run is ongoing. As long as it contains a token, the adjusted transitions of $N_1$ are live and can be used normally. Thus any marking which is reachable in the places of $N_1$ is also reachable in the corresponding places of $N_2$.
We add an additional transition $t_{p_a}$ %\alain{s est d'habitude un état}
which has $p_a$ as an input and a null output.
This allows to disable the transitions of $N_1$ and to "freeze" the marking of the places of $P_1$ in $N_2$.
 The place $p_a$ and transition $t_{p_a}$ allow the net $N_2$ to reach any reachable marking in $N_1$ and then for $t_{p_a}$ to fire and freeze the net at that marking.
We introduce a new place $p_b$ and new transitions $t_p$, for all $p \in P_1$, which have $p$ as input and $p_b$ as output.
Lastly, we add a transition $t_{p_b}$ with $p_b$ as its output and every place of $P_2$ as output, which ``floods'' the net with tokens, assuring that every transition is live if a token is ever
put in $p_2$.
\end{samepage}

@@

Indeed the marking with zero in every place of $P_1$ and in $p_b$ is reachable in $N_2$, by executing the same sequence of transition firings. Then $t_{p_a}$ can fire, leading to the marking which assigns zero to every place of $P_2$. From this marking the transitions $t_p$ are not live and neither are the transitions inherited from $N_1$ nor $t_{p_a}$, and, finally, nor is $t_{p_2}$. Thus $t_{p_2}$ is not live. \\

@@

Indeed, if $t_{p_2}$ is not live, then a marking $\mu$ must be reachable in which $\mu(p_2) = 0$ and there is no reachable state in which $p_2$ has a token (in particular, since we do not allow token removal from $p_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $p_2$).
This means that no transition $t_p$ is live in $\mu$ since any transition $t_p$ can place a token in $p_2$. 
Thus, every place of $P_2$ inherited from $N_1$ must be devoid of token. Moreover, since the marking $\mu$ must be reached  in a sequence of transitions that do not place any token in $p_2$, 
it can be reached without using the transitions $t_p$ or $t_{p_2}$. Since $t_{p_a}$ do not modify the places inherited from $P_1$ nor does it enable new transitions, the reachability of $\mu$ implies the reachability of a marking where every place of $P_2$ inherited from $P_1$ is devoid of token using only the transitions inherited from $N_1$. Thus the zero marking is reachable from $\mu_1$ in $N_1$.
\end{proof}
